%!TEX root = ../PhDThesis.tex


% *********************************************************************************************************************
% Acknowledgments
% *********************************************************************************************************************

\pdfbookmark[1]{Acknowledgments}{acknowledgments}
%
%\begin{flushright}{\slshape
%    We have seen that computer programming is an art, \\
%    because it applies accumulated knowledge to the world, \\
%    because it requires skill and ingenuity, and especially \\
%    because it produces objects of beauty.} \\ \medskip
%    --- \defcitealias{knuth:1974}{Donald E. Knuth}\citetalias{knuth:1974}~\citep{knuth:1974}
%\end{flushright}
%
%
%\bigskip
%
%\begingroup
%\let\clearpage\relax
%\let\cleardoublepage\relax
%\let\cleardoublepage\relax
\chapter*{Acknowledgements}

Firstly, I would like to sincerely thank my two supervisors at the University of Nottingham, Joel E. Fischer and Sarah Sharples. Joel, from the Mixed Reality Lab, and Sarah, from the Human Factors Research Group.
Both have provided continual encouragement, critique, support, care, and dedication to my work and personal development.
My sincere gratitude is also due to the countless friends and colleagues in the lab, especially Stuart Reeves, who have engaged (and some might say endured) numerous provocative discussions with me throughout my PhD.
Their critique, although difficult to receive at times, was ultimately always welcomed, appreciated, and most supportive.

The Horizon Centre for Doctoral Training, which supported me financially during this PhD, and the Mixed Reality Lab, where I have been based for the majority of the time, have always been welcoming and warm environments in which one can explore ideas, push boundaries, and develop a career.
I am grateful to both centres.

During this journey I met---and then married!---Juan Diego.
He has given me so much care, kindness, love, and support, and is a wonderful companion with whom I can explore the world and learn more about myself.
He makes the world seem less scary, always encourages me to stay focused when I need it, and continually empowers me to achieve my personal goals.
For this and so much more, I am unspeakably grateful. I love you.

My mother, Nicole, and father, Andrew, were both there for me whenever I needed them and they often realised I needed their help long before I did (although I am sure they feel I never need them anymore, but I assure them it is not true!).
As far I can remember they both have encouraged me to be bold and courageous because they believed in me and believed I could do what I set my sights on.
I am so dearly grateful for all the support and love they have given to me.
Thank you, both.

I would also like to thank (in alphabetical order, as there is no way I could order this list): Susan Ali, Kyle Arch, Pepita Barnard, Felicia Black, Jos\'{e} Gustavo Berumen Salazar, Liz Dowthwaite, Carolina Fuentes, Panagiotis Koutsouras, Shalaka Kurup, Horia Maior, Juan Pablo Mart\'{i}nez \'{A}villa, Annie Quandt, Richard Ramchurn, Andreas Reiter, Neelima Sailaja, Gareth Shaw, Jocelyn Spence, Sam Staple\-ford-Allen, Hanne Wagner, and Matt Wilkinson.
I am indebted to Andr\'es Lucero for offering and supporting me through my internship.
He provided wonderful insights into his work practices and always shared his valuable experiences and knowledge with me.
He has become a valuable colleague as well as a dear friend.

All of these people---and so many more---have shared so much of this journey with me and I have developed some truly cherished friendships.
Furthermore, to all of my friends and family, of which there too many to name here, who have been there for me throughout, and have celebrated my highs and helped me through the lows, your support and love made this all possible.

Finally, my thanks to the School of Computer Science and Mixed Reality Lab for supporting travel to CHI 2015 and 2016, MobileHCI 2015, and CSCW 2016 and 2017; the Horizon CDT, the Human Factors Research Group, and the Mixed Reality Lab for supporting travel and accommodation during my internship; and ACM SIGCHI and the university's Graduate School for supporting travel to CSCW 2017.
Ultimately, none of this would be possible without the Horizon Centre for Doctoral Training at the University of Nottingham (Grant No. EP/G037574/1) and by the Horizon Digital Economy Research Institute (Grant No. EP/G065802/1), who supported this project.


%\endgroup


% *********************************************************************************************************************
